Article title

### 2017-08-03 paper-webserver.tex

% 1. brief: WGS is standard
Whole genome sequencing (WGS) uses the entire genetic content of an organism, and is used for bacterial surveillance \cite{ronholm2016navigating,lytsy2017time}, research into disease \cite{wang2014whole,yuen2015whole}, and clinical diagnoses \cite{willig2015whole,dewey2014clinical}.
% 2. Big Problem: but tools are for individual analysis
Targeted software, such as the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive} for antimicrobial resistance (AMR) gene prediction, Prokka for bacterial genome annotation \cite{doi:10.1093/bioinformatics/btu153}, and integrated platforms, such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial} and the Integrated Rapid Infectious Disease Analysis (IRIDA) project \url{http://www.irida.ca/}, all leverage WGS data.
For bioinformatics software to reach true "big-data" goals, analyses modules must run in real-time and results must be integrated.
% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
WGS generates data at a break-neck speed; for \textit{Escherichia coli} alone, the public genome databases EnteroBase \url{https://enterobase.warwick.ac.uk/} and GenBank \cite{doi:10.1093/nar/gks1195} have 60,206 and 2,779,008 sequences uploaded, respectively.
Typical bioinformatics software, such as RGI and Prokka, take single files as input, and integrated platforms, such as BAP and IRIDA, build workflows linking different analyses modules.
BAP and IRIDA begin to solve "big-data" challenges by offering a hosted solution which computes results in real-time, and parallelizing analyses across computing resources.
For WGS to further benefit surveillance, research, and clinical fields, analyses results should also be integrated and searchable; storage of results would avoid recomputation, enable data persistence, and allow references to old analyses. \par

>>>>

% 1. brief: WGS is standard
Whole genome sequencing (WGS) uses the entire genetic content of an organism, and widely complements bacterial surveillance \cite{ronholm2016navigating,lytsy2017time}, research into disease \cite{wang2014whole,yuen2015whole}, and clinical diagnoses \cite{willig2015whole,dewey2014clinical}.
% 2. Big Problem: but tools are for individual analysis
Targeted software, such as the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive} for antimicrobial resistance (AMR) gene prediction, Prokka for bacterial genome annotation \cite{doi:10.1093/bioinformatics/btu153}, and integrated platforms, such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial} and the Integrated Rapid Infectious Disease Analysis (IRIDA) project \url{http://www.irida.ca/}, all leverage WGS data.
For bioinformatics software to reach true "big-data" goals, analyses modules must run in real-time and results must be integrated.
% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
WGS generates data at a break-neck speed; for \textit{Escherichia coli} alone, the public genome databases EnteroBase \url{https://enterobase.warwick.ac.uk/} and GenBank \cite{doi:10.1093/nar/gks1195} have 60,206 and 2,779,008 sequences uploaded, respectively.
Typical bioinformatics software, such as RGI and Prokka, take single files as input, and integrated platforms, such as BAP and IRIDA, build workflows linking different analyses modules.
BAP and IRIDA begin to solve "big-data" challenges by offering a hosted solution which computes results in real-time, and parallelizing analyses across computing resources.
For WGS to further benefit surveillance, research, and clinical fields, analyses results should also be integrated and searchable; storage of results would avoid recomputation, enable data persistence, and allow references to old analyses. \par
